\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{url}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{dirtytalk}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage[rightcaption]{sidecap}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}


\geometry{margin=1in}
\onehalfspacing

\title{\Large \textbf{Finance and the Unexpected}}

\author{
Saranya Anantapantula\\
\small University of Pennsylvania\\
Dr. Jessica Wachter\\
\small University of Pennsylvania - Finance Department
}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Extreme events in financial markets challenge traditional models built on volatility and normal distributions. Tail risks, model failures, and behavioral biases continue to drive persistent mispricing and systemic vulnerability. Prior research often relies on mean-variance frameworks, overlooking higher moments like skewness and kurtosis, as well as the limits of diversification under moral hazard. We use simulated jump-diffusion models, Monte Carlo experiments, and empirical return data to expose the underestimation of rare, severe shocks in asset pricing and in investor expectations. Option markets, credit derivatives, and debt instruments reveal embedded short-put-like structures that mask hidden risks. Behavioral insights from memory and context effects explain why investors lean on recent experience, misjudge tail probabilities, and fail to revise models even after crisis events. While short-term returns are marked by negative skewness and excess kurtosis, the long-run performance of public equities, enabled by regulation and broad risk-sharing, remains a surprising and underappreciated success.
\end{abstract}
% https://www.econometricsociety.org/publications/es-data-editor-website/package

\input{sec1}
\input{sec2}
\input{sec3}
\input{sec4}
\input{sec5}
\input{sec6}
\input{sec7}



\appendix
\section{Code and Data Availability} \label{appendix:code}

All the code and data used in this study are available at the following GitHub repository: \\
\url{https://github.com/anantapantulasa/unexpected_finance}


\bibliographystyle{plainnat} % can replace with apa or mla! 
\bibliography{references}

\end{document}